---
title: "Contributors"
subtitle: "The people behind ggseg"
---

```{r}
#| include: false
source("R/fetch-data.R")
contributors <- get_contributors()
```

## Core Team

The ggseg suite is primarily developed and maintained by [Athanasia Mo Mowinckel](https://drmowinckels.io), and core concept and initial prototype by [Didac Vidal-Piñeiro](https://www.sv.uio.no/psi/personer/vit/didacvp/).

## All Contributors {.section-header}

Thank you to everyone who has contributed to the ggseg ecosystem.

::: {.contributor-grid}

```{r}
#| echo: false
#| output: asis
for (i in seq_len(nrow(contributors))) {
  contrib <- contributors[i, ]
  cat(sprintf(
    '
::: {.contributor-card}
[![](%s)](https://github.com/%s){target="_blank"}
[%s]{.name}  
[%d contributions]{.contributions}
:::
',
    contrib$avatar_url,
    contrib$user,
    contrib$user,
    contrib$contributions
  ))
}
```

:::

## How to Contribute

We welcome contributions of all kinds:

- **Bug reports**: Found a bug? [Open an issue](https://github.com/ggseg/ggseg/issues)
- **Feature requests**: Have an idea? [Start a discussion](https://github.com/orgs/ggseg/discussions)
- **Code contributions**: Check out the [contribution guidelines](https://github.com/ggseg/ggseg/blob/main/.github/CONTRIBUTING.md)
- **New atlases**: Want to add a brain atlas? See [ggsegExtra documentation](https://ggseg.github.io/ggsegExtra/)
