---
title: "Packages"
---

```{r}
#| include: false
source("R/fetch-data.R")
core_packages <- get_core_packages()
atlas_packages <- get_atlas_packages()
```

## Core Packages {.section-header}

The foundational packages for brain atlas visualization in R.

::: {.package-grid}

```{r}
#| echo: false
#| output: asis
for (i in seq_len(nrow(core_packages))) {
  pkg <- core_packages[i, ]
  desc <- if (!is.na(pkg$description)) pkg$description else pkg$title
  status_class <- if (!is.na(pkg$status) && pkg$status == "success") "status-ok" else "status-fail"
  status_icon <- if (!is.na(pkg$status) && pkg$status == "success") "OK" else "!"
  logo_html <- if ("logo" %in% names(pkg) && !is.na(pkg$logo)) {
    sprintf('![](%s){.pkg-logo}', pkg$logo)
  } else {
    ""
  }
  cat(sprintf('
::: {.package-card}
%s

### %s
[v%s]{.version} [%s]{.build-status .%s}

[%s]{.description}

::: {.links}
[Docs](%s){target="_blank"} | [GitHub](%s){target="_blank"}
:::
:::
', logo_html, pkg$package, pkg$version, status_icon, status_class, desc, pkg$pkgdown_url, pkg$github_url))
}
```

:::

## Atlas Packages {.section-header}

Brain atlas datasets compatible with ggseg and ggseg3d. Each package provides polygon and/or mesh data for specific brain parcellations.

### Installation

Install any atlas package from R-universe:

```r
install.packages(
 "ggsegYeo2011",
 repos = c(
   "https://ggseg.r-universe.dev",
   "https://cloud.r-project.org"
  )
)
```

### Available Atlases

::: {.atlas-grid}

```{r}
#| echo: false
#| output: asis
for (i in seq_len(nrow(atlas_packages))) {
  pkg <- atlas_packages[i, ]
  status_class <- if (!is.na(pkg$status) && pkg$status == "success") "status-ok" else "status-fail"
  status_icon <- if (!is.na(pkg$status) && pkg$status == "success") "OK" else "!"
  logo_html <- if ("logo" %in% names(pkg) && !is.na(pkg$logo)) {
    sprintf('![](%s){.pkg-logo}', pkg$logo)
  } else {
    ""
  }
  cat(sprintf('
::: {.atlas-card}
%s

#### %s
[v%s]{.version} [%s]{.build-status .%s}

[Docs](%s){target="_blank"} | [GitHub](%s){target="_blank"}
:::
', logo_html, pkg$package, pkg$version, status_icon, status_class, pkg$pkgdown_url, pkg$github_url))
}
```

:::

## All Packages on R-universe

Browse all ggseg packages on [R-universe](https://ggseg.r-universe.dev/builds){target="_blank"} for detailed build status, documentation, and installation instructions.
